---
title: "Activity: Nuclear Reactors"
author: "Cael Walter"
output: html_notebook
---

```{r}
library(tidyverse)

```

## Scrape the Data 

```{r}
#My code here.... 

library(rvest)
library(dplyr)
library(lubridate)
library(ggplot2)


page <- read_html("https://en.wikipedia.org/wiki/List_of_commercial_nuclear_reactors")
tableList <- page %>%
  html_nodes(css = "table") %>%
  html_table(fill = TRUE)




length(tableList)

head(tableList[[21]])

japan_table <- tableList[[21]]


head(japan_table)


```


## Your turn: In what ways is the table tidy? How is it not tidy? What’s different about it from a tidy table?

My answer here..... 
1. Single Data Type per Column: Each column in the table contains a single type of data (e.g., reactor names, unit numbers, types, capacities, dates).
2. Consistent Units: Numerical values, such as capacity in megawatts (MW), are consistently used throughout the table.
3. Header Row: The table has a clear header row that labels each column, making the data easier to understand and work with.

In What Ways is the Table Not Tidy?
1. Non-Standard Header Row: The first row of the table is a continuation of the variable names, which should be part of the header instead of the data.
2. Mixed Data Types in Columns: Some columns may contain mixed data types (e.g., numerical and textual descriptions in the "Status" column).
3. Redundant Variable Names: Some variable names are redundant, such as having both "Capacity (MW)" and "Capacity in MW."
4. Multiple Words in Column Names: Column names with spaces and special characters can complicate data manipulation.

Differences from a Tidy Table
A tidy table, as defined in the principles of tidy data, should have the following characteristics:

Each Variable is a Column: In the given table, this principle is followed reasonably well.
Each Observation is a Row: The table mostly adheres to this principle, but the presence of non-data rows (like the continuation of the header) violates this rule.
Each Type of Observational Unit Forms a Table: This table mixes different types of data (such as reactor specifications and operational statuses), which might be better organized into separate tables for clarity.


## Your Turn: Plot Net Generation Capacity vs Construction Date

```{r}
#my code here 

japan_table_clean <- japan_table %>%
  slice(-1) %>%  
  rename(
    name = `Plantname`,
    unit_no = `UnitNo.`,
    reactor_type = `Type`,
    reactor_model = `Model`,
    status = `Status`,
    capacity_mw = `Capacity(MW)`,
    begin_building = `Beginbuilding`,
    commercial_operation = `Commercialoperation`,
    closure = `Closed`
  ) %>%
  mutate(
    capacity_mw = as.numeric(capacity_mw),
    begin_building = dmy(begin_building),
    commercial_operation = dmy(commercial_operation),
    closure = dmy(closure)
  )


head(japan_table_clean)

# Plot Net Generation Capacity vs. Construction Date
ggplot(japan_table_clean, aes(x = begin_building, y = capacity_mw, color = reactor_type)) +
  geom_point() +
  labs(title = "Net Generation Capacity vs. Construction Date",
       x = "Construction Start Date",
       y = "Net Generation Capacity (MW)") +
  theme_minimal()






```


## Your Turn: Scrape & Clean China Data (then merge with Japan)

```{r}
#my code here... 

china_table <- tableList[[10]]  


head(china_table)


china_table_clean <- china_table %>%
  slice(-1) %>%  # Remove the first row which is not data
  rename(
    name = `Plantname`,
    unit_no = `UnitNo.`,
    reactor_type = `Type`,
    reactor_model = `Model`,
    status = `Status`,
    capacity_mw = `Capacity(MW)`,
    begin_building = `Beginbuilding`,
    commercial_operation = `Commercialoperation`,
    closure = `Closed`
  ) %>%
  mutate(
    capacity_mw = as.numeric(capacity_mw),
    begin_building = dmy(begin_building),
    commercial_operation = dmy(commercial_operation),
    closure = dmy(closure)
  ) %>%
  mutate(country = "China")


japan_table_clean <- japan_table_clean %>%
  mutate(country = "Japan")



japan_table_clean <- japan_table_clean %>% 
  mutate(unit_no = as.character(unit_no))

china_table_clean <- china_table_clean %>%
  mutate(unit_no = as.character(unit_no))


combined_table <- bind_rows(
  japan_table_clean %>% mutate(country = "Japan"), 
  china_table_clean %>% mutate(country = "China")
)

head(combined_table)

```



## Your Turn: Reconstruct Info Graphic of Japan Reactors (or other country of interest)

```{r}
#My code here
ggplot(japan_table_clean, aes(x = begin_building, xend = commercial_operation, y = name, yend = name)) +
  geom_segment(aes(color = reactor_type), size = 1) +
  labs(title = "Time Interval from Start of Construction to Operation",
       x = "Date",
       y = "Reactor Name") +
  theme_minimal()
```